### 2016-04-30 ch01-intro/introduction.tex
Some intro work

\section{System idenfication}

\begin{figure}
  \centering
  \includegraphics[width=0.9\columnwidth]{\thisDir/figs/id-cycle.pdf}
  \caption[Identification loop]{Typical system identification loop. Figure based on \citep[Figure 1.10]{Ljung1999}.}
  \label{fig:intro:identification-cycle}
\end{figure}

@@

In this dissertation, the focus lies on \gls{LTI} systems.
While this might seem as a very restrictive choice, this is one of the fundamental settings for system identification.
In particular, \gls{LTI} systems are a first step for many people to build a system model.
In many cases, such a linear model is accurate enough, e.g. to build a nominal controller, to design electrical filters and obtain a reasonable intuition of the system under test.
When such a linear model is not adequate, a more flexible model, e.g. a time-varying model, a nonlinear model or parameter-varying model needs to be constructed.
However, many of those advanced modeling approaches build upon \gls{LTI} models.
As such, improvements in estimating \gls{LTI} models also indirectly benefit more advanced models.

>>>>

\section{System Idenfication}

System identification is the scientific approach of converting observations of a system into mathematical models that describe the behavior of the system under test.
In \figref{fig:intro:identification-cycle}, a high-level flow diagram containing some key steps that are performed when identifying a system.
Note that this is a simplified view, different authors

\begin{figure}
  \centering
  \includegraphics[width=0.9\columnwidth]{\thisDir/figs/id-cycle.pdf}
  \caption[System identification loop]{System identification loop. \disclaimer{Adapted from \citep[Figure 1.10]{Ljung1999} and \citep{Mehra1981}.}}
  \label{fig:intro:identification-cycle}
\end{figure}

@@

In this dissertation, the focus lies on \gls{LTI} systems.
While this might seem as a very restrictive choice, this is one of the fundamental settings for system identification.
In particular, \gls{LTI} systems are a first step to build a system model.
In many cases, such a linear model is accurate enough, e.g. to build a nominal controller, to design electrical filters and obtain a reasonable intuition of the system under test.
Also, most engineers and scientists have a good understanding of linear systems such that \gls{LTI} models align well with their prior knowledge and experience.
Nevertheless, when a linear model is not adequate, a more flexible model needs to be constructed.
Such a model could be more flexible, e.g. by relinquishing the time-invariance and/or its linearity.
However, many of those advanced modeling approaches employ \gls{LTI} models as starting values or intermediate result in building the actual non-linear~\citep{Giri2010} or time-varying model~\citep{Lataire2012,Louarroudi2014}.
As such, improvements in estimating \gls{LTI} models also indirectly improve more advanced methods.

\subsection{Contributions}
In this dissertation, we look into a few aspects of the identification workflow with the goal to make the whole process more user-friendly.

\paragraph{How should a good experiment be designed?}
Can we design a `good experiment' to identify a \gls{LTI} model?
Particularly, this means a robust input signal needs to be constructed without relying on extensive prior knowledge of the system.
Such a signal should cover a wide frequency band to excite all dynamics of the system during the experiment.
However, the signal should ensure that systems in different frequency bands can be identified with a specified level of accuracy.

\paragraph{Can we process the input/output data in a non-parametric way that offers more insight than a standard frequency response function?}

\paragraph{Can we }
